Differential Expression - MSSM-Penn-Pitt - ACC DLPFC - Dx.Tissue

### 2020-04-27 MSSM-Penn-Pitt_DE_DxTissue.Rmd
fix random effects syntax in formula

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx.Tissue", "RIN2", "(1|Institution)", "ageOfDeath", "EV.1", "PMI", "(1|Reported_Gender)", "EV.4","EV.2","RIN", "EV.3", "EV.5", "IntronicRate")
```

@@

```{r iterative.normalisation, results='asis'}
writeLines(paste('Using following covariates in the model:',
                 paste(adjust.covars, collapse=', '),
                 'as fixed effects and Individual_ID is chosen as random effect'))

# Post adjusted formula
random_effect <- "Individual_ID"
formula <- glue::glue("~ ", glue::glue_collapse(adjust.covars, sep = " + ")) %>% 
  glue::glue(" + (1|{random_effect})")

@@

col_type <- dplyr::select(COVARIATES, c(adjust.covars, "Individual_ID")) %>%
  dplyr::summarise_all(class) %>% 
  tidyr::gather(variable, class)

@@

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + ")) %>% 
  glue::glue(" + (1|{random_effect})")
```

>>>>

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx.Tissue", "RIN2", "ageOfDeath", "EV.1", "PMI", "EV.4","EV.2","RIN", "EV.3", "EV.5", "IntronicRate")
random_effect <- c("Individual_ID", "Institution", "Reported_Gender")
```

@@

```{r iterative.normalisation, results='asis'}
writeLines(glue::glue('Using following covariates in the model:',
                 glue::glue_collapse(adjust.covars, sep = ", ", last = " and "),
                 ' as fixed effects and',
                 glue::glue_collapse(random_effect, sep = ", ", last = " and "),' chosen as random effects'))

# Post adjusted formula
formula <- glue::glue("~ ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))

@@

col_type <- dplyr::select(COVARIATES, c(adjust.covars, random_effect)) %>%
  dplyr::summarise_all(class) %>% 
  tidyr::gather(variable, class)

@@

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))

```
